Abalone Performance Measures

### 2020-05-26 data-raw/Tas_HS_PMs.Rmd
Correccted getgrad4 and modified getscore1 into getscore, which now works for both grad PMs.

```{r echo=TRUE, plot.width=5.75, plot.height=2.75}
# round the range to get workable numbers
bounds <- round((range(grad1,na.rm=TRUE) * 1.1),2)
low <- seq(bounds[1],0.0,length=6) 
high <- seq(0.0,bounds[2],length=6)
xax <- c(low[1:5],high)  # combine above with below zero
xax2 <- seq(-0.32,0.32,length=11)
wrong <- lm(0:10 ~ xax2)
par(cex=0.9,font.axis=7,font=7,font.lab=7)
plot(xax,0:10,type="n",xaxt="n",xlab="Gradient1 Value",yaxt="n",
     ylab="Gradient1 Score")
axis(side=1,at=xax,label=xax)     # need to define the axes independently
axis(side=2,at=0:10,label=0:10)   
abline(v=xax,lwd=1,col="grey",lty=3)
abline(h=0:10,lwd=1,col="grey",lty=3)
abline(wrong,lty=2)
lines(c(-0.23,0.0),c(0,5),lwd=2)  # add the linear relationships
lines(c(0.0,0.32),c(5,10),lwd=2)
score1 <- getscore1(grad1)  # examine the code using getscore1 without brackets
points(grad1,score1,pch=16,col=2,cex=1.5)
```

@@

```{r  echo=TRUE}
grad4 <- getgrad4(grad1,wid=4) # uses five years of data; red in the figure 
grad3 <- getgrad4(grad1,wid=3) # uses four years of data; blue in the figure
range(grad4)
range(grad3)
```

```{r  echo=TRUE, plot.width=5.75, plot.height=2.75}
#plotprep(width=7,height=5,newdev=FALSE)
parset(plots=c(2,1))
plot(ab$year,ab$cpue,type="l",lwd=2,ylim=c(0,100))
plot(0:27,c(NA,grad1),type="l",lwd=2)        # black
lines(0:27,c(NA,NA,NA,NA,grad4),col=2,lwd=2) # red
lines(0:27,c(NA,NA,NA,grad3),col=4,lwd=2)    # blue
abline(h=0.0,col=3)

@@

>>>>

```{r echo=TRUE, plot.width=5.75, plot.height=2.75}
# round the range to get workable numbers
bounds <- round((range(grad1,na.rm=TRUE) * 1.1),2)
low <- seq(bounds[1],0.0,length=6) 
high <- seq(0.0,bounds[2],length=6)
xax <- c(low[1:5],high)  # combine above with below zero
xax2 <- seq(-0.32,0.32,length=11)
wrong <- lm(0:10 ~ xax2)
par(cex=0.9,font.axis=7,font=7,font.lab=7)
plot(xax,0:10,type="n",xaxt="n",xlab="Gradient1 Value",yaxt="n",
     ylab="Gradient1 Score")
axis(side=1,at=xax,label=xax)     # need to define the axes independently
axis(side=2,at=0:10,label=0:10)   
abline(v=xax,lwd=1,col="grey",lty=3)
abline(h=0:10,lwd=1,col="grey",lty=3)
abline(wrong,lty=2)
lines(c(-0.23,0.0),c(0,5),lwd=2)  # add the linear relationships
lines(c(0.0,0.32),c(5,10),lwd=2)
score1 <- getscore(grad1)  # examine the code using getscore1 without brackets
points(grad1,score1,pch=16,col=2,cex=1.5)
```

@@

```{r  echo=TRUE}
grad4 <- getgrad4(ab$cpue,wid=4) # uses five years of data; red in the figure 
grad3 <- getgrad4(ab$cpue,wid=3) # uses four years of data; blue in the figure
range(grad1)
range(grad4)
range(grad3)
```

```{r  echo=TRUE, plot.width=5.75, plot.height=2.75}
#plotprep(width=7,height=5,newdev=FALSE)
parset(plots=c(2,1))
plot(ab$year,ab$cpue,type="l",lwd=2,ylim=c(0,100))
plot(0:27,c(NA,grad1),type="l",lwd=2,ylim=c(-0.21,0.29))        # black
lines(0:27,c(NA,NA,NA,grad4),col=2,lwd=2) # red
lines(0:27,c(NA,NA,grad3),col=4,lwd=2)    # blue
abline(h=0.0,col=3)

@@

```{r  echo=TRUE, plot.width=5.75, plot.height=2.75}
# round the range to get workable numbers
bounds <- round((range(grad4,na.rm=TRUE) * 1.1),2)
low <- seq(bounds[1],0.0,length=6) 
high <- seq(0.0,bounds[2],length=6)
xax <- c(low[1:5],high)  # combine above with below zero
xax2 <- seq(-0.31,0.31,length=11)
wrong <- lm(0:10 ~ xax2)
par(cex=0.9,font.axis=7,font=7,font.lab=7)
plot(xax,0:10,type="n",xaxt="n",xlab="Gradient4 Value",yaxt="n",
     ylab="Gradient4 Score")
axis(side=1,at=xax,label=xax)     # need to define the axes independently
axis(side=2,at=0:10,label=0:10)   
abline(v=xax,lwd=1,col="grey",lty=3)
abline(h=0:10,lwd=1,col="grey",lty=3)
abline(wrong,lty=2)
lines(c(-0.15,0.0),c(0,5),lwd=2)  # add the linear relationships
lines(c(0.0,0.31),c(5,10),lwd=2)
score4 <- getscore(grad4)  # examine the code using getscore1 without brackets
points(grad4,score4,pch=16,col=2,cex=1.5)

```{r}
cbind(score1,c(NA,NA,score4))
```

```{r  echo=TRUE, plot.width=5.75, plot.height=2.75}
years <- 1993:2019
score42 <- c(NA,NA,score4)
parset()
plot(years,score1,type="p",pch=16,cex=1.25,panel.first=grid(),
     ylim=c(0,10),ylab="Score 1 and 4")
lines(years,score1,lwd=1)
points(years,score42,type="p",pch=16,cex=1.25,col=2)
lines(years,score42,lwd=1,col=2)
abline(h=5.0,col=3)
legend("topright",c("score1","score4"),col=c(1,2),lwd=3,bty="n",cex=1.5)
```

```{r}
